\section{Further work following progression}
\protect\label{section:worktocome}

The following is the programme of work I need to undertake in order to regard
the project as complete.

In a lot of cases, the work already done will need revisiting and refining and
``iterating until convergence'' achieved.

I see the following as necessary.

\begin{enumerate}
  \item Better handle bad or unreliable pixels identifying ones prone to
  ``spikes'' and bouts of insensitivity and improving the interpolation over
  them. Where they land on an object, it would be better to interpolate using
  any fitted Gaussian profile.
  \item Optimise as many as possible of the reference object apertures and
  identify irregularly shaped and variable objects and ones flagged in GAIA as
  having poor RUWE and LUWE.
  \item Look at other filters, such as the \gfilter, possibly the other filters,
  although the number of available reference objects looks poor and the
  {\zfilter} images all have artefacts in them.
  \item Refine the linearity correction, the restriction to above 5,000 ADU
  counts (and less importantly below 62,000 counts) is acceptable for selection
  of daily flat fields, but for the bulk of the objects on the frames, needs
  to be properly catered for.
  \item Repeat the work done for {\ross} with {\prox} and {\bstar} and consider
  periodograms for them. In particular, obtain a rotation period for \bstar,
  for which there are a variety of values in the literature.
  \item Extend the work done to date to the REMIR near infrared images.
\end{enumerate}

I intend to spend the period until the end of the calendar year focusing on
steps 1 and 2, before moving on to 3, to complete the analysis of {\ross} and
making the techniques more automatic, particularly in the area of
fitting of reference objects and optimising the apertures, which relies
currently on too much manual intervention to be viable.

The year to the end of 2023 should see the balance of the project completed
ready for write-up and submission by April 2024.

\Notnow{
\section{Accuracy}
\protect\label{section:accuracy}

It seemed worth looking at whether any adjustments of the exposure times might
improve the accuracy, as many of the objects which might be used for reference
give an ADU count only just above the sky level. The exposure times currently
are 10 seconds for {\prox} and {\ross} and 5 seconds for \bstar.

Table \ref{table:pixvals} is set out the maximum value in any of the observation
files for each target and each filter and the percentage of observation files in
which at least one pixel exceeds a give number of ADUs (this does not currently
take account of defective pixels or cosmics, but these would have negligible
effects on the results).

It is clear that some increase in exposure time, possibly up to 5 times or more
in the case of the \gfilter, would benefit the contrast, except
for the {\ifilter} results, which are generally too close to saturation.
The nature of the instrument, however, may not permit any different exposure
times to be made with different filters.

\begin{table}[!htbp]
\begin{center}
\begin{tabular}{|l|r|rrrr|} \hline
Filter & Max value & \% over 30,000 & \% over 40,000 & \% over 50,000 & \% over
60,000 \\\hline
 \multicolumn{6}{|c|}{\textbf{\bstar} exp 5 sec} \\\hline
\texttt{g} & 63,422 & 0.05 & 0.05 & 0.05 & 0.05 \\
\texttt{i} & 63,448 & 78.94 & 61.15 & 45.71 & 0.77 \\
\texttt{r} & 54,806 & 16.68 & 3.73 & 0.97 & 0.00 \\
\texttt{z} & 63,387 & 12.52 & 3.37 & 0.87 & 0.05 \\
\hline
\multicolumn{6}{|c|}{\textbf{\prox} exp 10 sec} \\\hline
\texttt{g} & 63,466 & 0.38 & 0.30 & 0.25 & 0.18 \\
\texttt{i} & 63,457 & 74.15 & 52.88 & 36.84 & 4.03 \\
\texttt{r} & 63,425 & 0.60 & 0.10 & 0.09 & 0.08 \\
\texttt{z} & 63,456 & 25.38 & 11.64 & 5.47 & 0.16 \\
\hline
\multicolumn{6}{|c|}{\textbf{Ross 154} exp 10 sec} \\\hline
\texttt{g} & 63,453 & 0.41 & 0.35 & 0.28 & 0.22 \\
\texttt{i} & 63,452 & 76.71 & 57.35 & 39.25 & 2.16 \\
\texttt{r} & 63,268 & 7.99 & 2.38 & 0.93 & 0.11 \\
\texttt{z} & 63,447 & 8.33 & 2.14 & 0.45 & 0.04 \\
\hline
\hline
\end{tabular}
\end{center}
\caption{This figures shows the maximum ADU values of any pixel in any of the
observation files for each of the 3 {\rdwarf} targets for each filter. The
following columns show the percentage of pixels in each case which are above
30,000, 40,000, 50,000 and 60,000.}.
\protect\label{table:pixvals}
\end{table}
\clearpage
}